Clustering by category and plots

### 2024-09-27 data/04-bycategoriy-clustering.qmd
small edits and knitted the half done draft

```{r}
df_DA <- df |> left_join(access_15 |> dplyr::select(c("from_id","GeoUID")), by = "from_id") |> 
  group_by(GeoUID) |> 
  summarise(
    SC1 = median(SC1),
    SC2 = median(SC2),
    SC3 = median(SC3),
    SC4 = median(SC4),
    SC5 = median(SC5),
    SC6 = median(SC6),
    SC7 = median(SC7),
    parcel_count = n_distinct(from_id),
    max_label_val = pmax(SC1, SC2, SC3, SC4, SC5, SC6, SC7),
    div_allcats = median(div_allcats),
    Total_copp_groc = median(Total_copp_groc),
    Total_copp_dep = median(Total_copp_dep),
    Total_copp_health = median(Total_copp_health),
    Total_copp_err = median(Total_copp_err)) |>
  mutate(max_label = case_when(max_label_val == SC1 ~ "a. Very caring - very complete (SC1)",
                               max_label_val == SC2 ~ "b. Very caring - mostly complete (SC2)",
                               max_label_val == SC3 ~ "d. Somewhat caring - mostly complete (SC3)",
                               max_label_val == SC4 ~ "c. Very caring - mostly complete (SC4)",
                               max_label_val == SC5 ~ "j. not caring - somewhat complete (SC5)",
                               max_label_val == SC6 ~ "e. Somewhat caring - mostly complete (SC6)",
                               max_label_val == SC7 ~ "f. not caring - not complete (SC7)"))

>>>>

Not caring - not complete (C7)
Somewhat caring - not complete (C4)
Somewhat caring - complete (C5)
Caring - somewhat complete (C3)
Caring - very complete (C6)
Very caring - complete (C2)
Very caring - very complete (C1)

```{r}
df_DA <- df |> left_join(access_15 |> dplyr::select(c("from_id","GeoUID")), by = "from_id") |> 
  group_by(GeoUID) |> 
  summarise(
    SC1 = median(SC1),
    SC2 = median(SC2),
    SC3 = median(SC3),
    SC4 = median(SC4),
    SC5 = median(SC5),
    SC6 = median(SC6),
    SC7 = median(SC7),
    parcel_count = n_distinct(from_id),
    max_label_val = pmax(SC1, SC2, SC3, SC4, SC5, SC6, SC7),
    div_allcats = median(div_allcats),
    Total_copp_groc = median(Total_copp_groc),
    Total_copp_dep = median(Total_copp_dep),
    Total_copp_health = median(Total_copp_health),
    Total_copp_err = median(Total_copp_err)) |>
  mutate(max_label = case_when(max_label_val == SC1 ~ "a. Very caring - very complete (SC1)",
                               max_label_val == SC2 ~ "b. Very caring - mostly complete (SC2)",
                               max_label_val == SC3 ~ "d. Somewhat caring - mostly complete (SC3)",
                               max_label_val == SC4 ~ "c. Very caring - mostly complete (SC4)",
                               max_label_val == SC5 ~ "j. Somewhat caring - somewhat complete (SC5)",
                               max_label_val == SC6 ~ "e. Somewhat caring - not complete (SC6)",
                               max_label_val == SC7 ~ "f. not caring - not complete (SC7)"))
